\section{User manual}
\subsection{Initial setting}
To set both the current time and the awake time the user can use the two buttons provided by the board. Both the setting procedures comprise two steps:
\begin{itemize}
	\item set hours, and
	\item set minutes.
\end{itemize}
Seconds are always supposed to start from zero (0). Below is the procedure to follow:
\begin{enumerate}
	\item Press \textbf{BUT2} to set the hours value;
	\item Press \textbf{BUT1} to save the value, and start setting the minutes;
	\item Press \textbf{BUT2} to set the minutes value;
	\item Press \textbf{BUT1} to save the current time and start setting the awake time.
\end{enumerate}
The procedure for setting the awake time is the same. The board displays two different messages according to the actual procedure, as follows:
\begin{itemize}
	\item \textit{Enter the time}, for the current time;
	\item \textit{Enter the awake time}, for the awake time.
\end{itemize}
Once completed the initial settings, the display shows the time, in the format \textit{hh:mm:ss}. Every second the display is updated, and \textbf{LED0} (yellow) blinks to show the flowing time. Its period is set to half a second.

\subsection{Change current or awake time}
Users cannot modify an already saved value during the initial setting. In order to correct mistakes, a user has to complete the procedure and then modify specifically the wrongly-provided time. This can be done using the two buttons, with the following mapping:
\begin{itemize}
	\item \textbf{BUT1} allows the user to modify the current time, and
	\item \textbf{BUT2} allows the user to modify the awake time.
\end{itemize}
The steps to follow are the same as the aforementioned ones. The display shows a different message according to the actual chosen procedure. If the current time changes, seconds restart from zero. Otherwise, if the wake up time changes, seconds remain untouched.

\subsection{Ringing}
Ringing is replaced by blinking \textbf{LED1} (red). The blinking duration is set to 30 seconds. After that the led stops blinking and the timer will wake up after 24 hours, unless the user sets it differently.

